\textbf{Optimization of Porous Silicon Gradient Refractive Index Structures.}

### 2020-06-15 paper.tex
Revise upto fig. 7

Keywords: Porous Silicon; GRIN; Reflectance Spectra.
\end{abstract}
\notaL{Cambié el abstract, pero habrá que revisarlo después.}
\section{Introduction}

\notaL{No entiendo nada de la introducción}
The structural properties of nanostructured materials  has  received a
considerable attention,  and a large research effort has been devoted
to them \cite{I1}. We found a great way to go for future
technological  explorations,  countless  challenges and  that  open a
range of possibilities to develop further  study  on these
issues\cite{I2}. Porous silicon (PS) is a versatile nanostructured
material and an excellent candidate as a technological platform for
different sensing applications \cite{I3, I4}, due to its easy
manufacturing,  large surface area, high surface reactivity,  and
moreover, its optical transduction capacity.  Photonic crystals are
multilayer dielectric structures that have periodicity in the
dielectric function along one direction \cite{I5}. It has numerous
studies for high reflectivity and the ability to adjust  the photonic
prohibited  band (PBG)\cite{I6} , which leads to possible applications
such as filters\cite{I7}, optical switches\cite{I8}, omnidirectional
mirrors\cite{I9}, waveguides for PC \cite{I10} etc. In the
conventional manufacturing of PS the desired result  is to obtain
homogeneous samples (same structural characteristics) from the
periphery  to the center  of the electrochemically  attacked area.
However, with an asymmetric anodizing configuration,  samples with a
lateral gradient in terms of pore size and thickness of the porous
layer are obtained \cite{I101}. In this configuration,  the face of
the platinum  electrode (cathode)  is relatively maintained
perpendicular  to the surface of the Si substrate (anode) at one end
of the cell, so that the distribution of the current within the
electrolyte  solution varies depending on the distance  of the
electrode due to the resistance of the electrolyte,  resulting  in a
decrease in current density as the distance from the electrode
increases \cite{I102, I103}. The result is a porous surface with
different pore sizes ranging from a few nanometers  to pores on the
order of a few micrometers  \cite{I104}. The dimensions of the pores
obtained on the same chip can be controlled by adjusting the anodizing
current and electrolyte concentration \cite{I11}. Currently, these
types of samples have found their application relevant as optical band
filters \cite{I12}, devices with a multidirectional photonic band
(photonic bar codes) \cite{I13} and mainly as biosensors. In this way,
the effect of different topographies (porosities in the same sample)
on the culture / adhesion of certain cells \cite{I14} is studied,
considerably reducing the number of samples and cost of the study. In
addition, they are also very useful when a biomolecule size-exclusion
technique is required allowing the identification and separation of
these biological compounds \cite{I15}. Recent studies  have shown that
the  combination  of thermal  oxidation  and infiltration of TiO2   by
ALD offers the  opportunity to manufacture  a high index of refraction
of contrast, visibly transparent GRIN optical elements from PS
absorbent structures \cite{I16}. A Despite previous research on the
formation of porous silicon with GRIN, type p in manufacturing and
characterization, there was no control of current densities, much less
a model that  explained said lateral  gradient. In this work, we
reported a gradient refractive index (GRIN) structure by varying the
current density on the fabrication of porous silicon photonic
structure. This current density values, depth, and porosity of the
photonic structure were calculated from an electrostatic model for
photonic crystals with a gradient refractive index
(EMPCGRIN). Moreover, the theoretical and experimental studies were
exhibited similar results.

@@

\section{Theory}
\subsection{Calculation of the current density}
\notaL{check where acronyms are first defined}
A gradient in the optical properties of porous Silicon (PS) systems may be
obtained by electrochemically attacking a Si surface with a position dependent current
density ${\bm j(\bm r)}$, as the porosity and refractive index depend on
the current density, as well as the speed of attack and the width of the
porous layer. Nevertheless, it is not a simple task to measure the
{\em local} value of $\bm j(\bm r)$ along the surface. This hampers the
design and optimization of well characterized reproducible GRIN PS
structures.\notaL{Tenemos referencias para afirmar esto?} Thus, we
believe a
system for which the current density field may be
easily computed would be useful.
Though $\bm j(\bm r)$ may be in principle be numerically calculated for a
given arbitrary experimental setup,  here we propose a particularly
simple setup that allows an expression for the current in terms
of a series that is rapidly convergent and each of whose terms is a
simple analytic function. With this setup it is easy to characterize
the dependence of different properties of interest on the current, and
this allows the design and optimization of diverse GRIN PS devices.

@@

\section{Procedures}
\begin{figure}
  \centering
  \includegraphics[width=.8\textwidth]{paper-3}\\[12pt]
  \includegraphics[width=.8\textwidth]{paper-4}\\[12pt]
  \includegraphics[width=.8\textwidth]{paper-5}
  % \\[12pt]
  % \includegraphics[scale=0.6]{Images/DE1}

@@

\subsection{Fabrication of PS  GRIN Single Layers}
We manufactured single layer PS structures through an electrochemical
anodization on a (100) $p$-type crystalline Si wafer
(resistivity 0.002 - 0.005 $ \Omega\,\text{cm}$), under galvanostatic
conditions. The process was performed at
room temperature,\notaL{Controlaste/mediste la temperatura?} with an
electrolytic mixture of aqueous hydrofluoric
acid (HF) (concentration: 48 $ \% $ wt), glycerol (purity: 99.8 $ \% $
wt) and ethanol (purity: 99.9 $ \%$ wt ) in a 3:7:1 volume ratio,
respectively. After the anodizing process, the samples were rinsed with
ethanol (purity: 99.9 $ \% $  wt). The electrolytic cell had the shape
of a rectangular prism as shown in Fig. \ref{fig:DE1}, with a base of
size $0.62\text{cm}\times2.03\text{cm}$) with an uncovered sample area
of $1.206\text{cm}^2$. \notaL{¿Cuáles fueron las coordenadas del
  electrodo?} We manufactured samples using a current $I=5\text{mA}$
which yielded current densities in the range
$j_\perp=2.5-6.0\text{mA}/\text{cm}^2$ and other smples using a larger
current $I=40\text{mA}$ corresponding to current densities in the
range $j_\perp=20-50\text{mA}/\text{cm}^2$. The cathode was a
platinum wire that with an approximate diameter of $0.5\text{mm}$.
\subsection{Morphological studies}
\notaL{Cambié el orden}
The morphologies of the etched porous layers were
observed using a Hitachi SU1510 scanning electron microscope (SEM)
with which we measured the thickness $d$ and the porosity $p$ of the
films at different positions along the sample from its top and side
views (Fig. \ref{fig:DE1}).

\subsection{Reflectance Measurement}
We measured the reflectivity spectra using a {\em Perkin Elmer Lambda 950}
UV-Vis-NIR spectrophotometer. For iterpretation of the data in the
case of a single PS layer we used
the standard formula \notaL{referencia} for three media air (0), PS
(1) and c-Si (2),
 \begin{eqnarray}\label{Eq:ECMR}
   R=\frac{r _ {_ {01}}r _ {_ {12}} e^{2i\delta}}{1+r _ {_ {01}}r _ {_ {12}} e^{2i\delta}}
\end{eqnarray}
where $ r_{01} $ y $ r_{12}$ are the Fresnel reflectance
coefficients at the air/PS and PS/c-Si interfaces \notaL{referencias}
and $\delta=k_{PS}^\perp d$, where $k_{PS}^\perp$ is
the component of the wavevector perpendicular to the surface within
the porous layer of width $d$.
\notaL{Me tienes que explicar dónde y cómo usaste lo que mencionas en
  la siguiente frase:
The advantage of this method is
the possibility of taking into account the interface roughness effect
by including the Davies-Bennett factor in the coefficient of each
Fresnel \cite{I17, I18, I19}, which represents the roughness of a
Gaussian distribution.}
\subsection{Refraction Index of PS GRIN Single Layers}
The local refractive index $n_{PS}$ of the PS layer was calculated from its
porosity $p$ through
Bruggeman's effective medium theory \cite{I20} \notaL{Elegir y checar:
  varepsilon o epsilon para funciones dieléctricas}
\begin{eqnarray}\label{Eq:Brugg}
 p\frac{1-\varepsilon_{PS}} {1+\varepsilon_{PS}} + (1-p)
  \frac{\varepsilon_{\text{Si}} - \varepsilon_{PS}}
  {\varepsilon_{\text{Si}}+\varepsilon_{PS}}
\end{eqnarray}
where the porosity $p$ is the volume fraction of air within the PS
layer, $\varepsilon_{Si}$ is the dielectric function of c-Si, and
$\varepsilon_{PS}=n_{PS}^2$ is the dielectric function of the PS.
\notaL{Quité frases irrelevantes.}
\subsection{Fabrication  of GRIN PS Microcavities}
After characterizing the preparation of single PS GRIN layers, we
fabricated PS GRIN microcavities (MC) as specific defects between two distributed Bragg
mirrors  (DBR). Alternate quarter wavelength plates of high (H) and low (L)
refractive indices $n_i$ of widths $d_i$, $i=H,L$ were prepared satisfying the Bragg condition
$n_id_i=\frac{\lambda_c}{4}$ at a given design
wavelength $\lambda_c$ and at a position $A$ (Fig. \ref{fig:DE1} which
we chose as that directly below the point-like electrode. The defect
was chosen as a half-wavelength low index layer of width $d_d$ such that
$n_Ld_L=\lambda_c/2$, and the MC has the
following sequence: $(HL)_6HH(LH )_6$. \notaL{Hay algo mal. La
  película de $\lambda/2$ fue de alto o de bajo índice? En una parte
  dices una cosa y en otra otra. ¿Será $(HL)_jHLLH(LH)_6$? ¿O será
  $(LH)_6LL(HL)_6$? ¡Muy descuidado!}
We chose $\lambda_c= 0.67 \mu\text{m}$. For the high index layers we
chose a current $I_H=5\text{mA}$ which corresponded to a current density
$j_{HA\perp}= 6\text{mA}/\text{cm}^2$ below the tip \notaL{checar}, and yielded
$n_H =2.6$, corresponding to a porosity \notaL{P mayúscula
  es porosidad, o p minúscula. Checar consistencia} $P_H =0.46$, and a
width $d_H=0.066 \mu\text{m}$, which required an attack time of
$t_H=35 \text{s}$. The corresponding parameters for the low density
layers were $I_L=38\text{mA}$, $j_{LA\perp}=50\text{mA}/\text{cm}^2$, $n_L= 1.4$,  $P_L =0.75$,
$d_L=0.117 \mu \text{m}$, and $t_L=11 \text{s}$. For the rest of the
sample the current density, porosity, index of refraction and width
varied, yielding a GRIN MC.

\section{Discussion and Results}
\subsection{Simulation of the EMPCGRIN model}
 To test the developed  idea in the theoretical section, we find a
 relation of the tip of the counter electrode that acts similarly as a
 point charge and the current density for a geometry in an
 electrolytic box and solve the electrostatic equations with suitable
 boundary conditions. Resulting in an electrostatic model for photonic
 crystals with a refractive index with gradient (EMPCGRIN).
\begin{figure}
  \centering
  \includegraphics[scale=0.7]{Images/G123}
  \caption{\emph{ Simulation to calculate the current density in
      a structure with gradient refractive index (GRIN) produced
      by electrochemical attack on crystalline silicon to
      produce porous silicon (PS), with a current density
      profile $ J (mA / cm ^ 2 ) $ normalized with the electric
      current $ I (mA) $, we have $ J / I \sim 0.5 \ \ a \ \ 1.2
      (cm^{-2}) $, for a cell of $ a = 2.03 \ \ cm $ y $ b =
      0.62 \ \ cm $, with an electrode height $ Z_0 = 0.96 \ \
      cm $} Eq. (\ref{Eq:J})}.
  \label{fig:DR1}
\end{figure}
We consider Fig. \ref{fig:DR1} which come from solving
Eq. (\ref{Eq:J}), calculating the current density as a function of the
rectangular cell area of $1,206 \ \ cm^2 $,  the programming with the
PERL PDL package and corresponding graph in gnuplot. We optimize the
appropriate values so that our current density adequately attacks
crystalline silicon, giving the gradient effect. We use as length $a =
2.03 \ \ cm $ and width $b = 0.62 \ \ cm $ the height of the solution
is $ c = 1 \ \ cm $ and we could locate the tip of the electrode at $
R_0 = (X_0 = 0.2 , \ \ Y_0 = 0.4 \ \, Z_0 = 0.96) \ \ cm $ and
evaluated at the surface on the silicon interface, in the plane $ Z =
0 $. In this same Figure \ref{fig:DR1}, we obtain a current density
profile $ J (mA / cm^2) $ normalized with the electric current $ I
(mA) $, we have $ J / I \sim 1.2 \ \ a \ \ 0.5 (cm ^{-2}) $, as we see
in Fig. \ref{fig:DR1} a) an effect that happens on the surface of the
sample, a change of contrate due to the different densities of
attacked currents. We see the decay behavior that the profile has as
Fig. \ref{fig:DR1} b) which is a cut on the axis of $ a $. When we
vary the currents we can observe the behavior of changes in the
normalized current density, with the data obtained through the
simulation we could have a better optimization in the design of porous
silicon proposing a new and novel experimental arrangement, in the
same way we can give ourselves an idea by means of the graph of how
the attack would be and the formal side of the pores in the silicon.

\subsection{Monolayers GRIN Porous Silicon }
	\includegraphics[scale=.3]{Images/celdan2}
	\caption{\emph{ Mechanical 3D modeling, design of the
            electrochemical cell where we can see the shape of a prism
            giving the required and necessary data for the
            experiments. The design of the cell used is $ 1,206 \ \ cm
            ^ 2 $ (this is the area attacked in the process), the area
            attacked is rectangular ($ 0.62 \ \ cm \times 2.03 \ \ cm
            $) and a height ( $ 1.2 \ \ cm $) a) Complete cell b) Cell
            without top cover and c) Top view}}
	\label{fig:por1}
We can see in Fig. \ref{fig:por1}, 3D modeling the mechanical design
for the electrochemical cell  better optimization in manufacturing
silicon pores where we can see the shape of a prism giving the
required data. The design of the cell used is $ 1,206 \ \ cm ^ 2 $
(this is the area attacked in the process), the area attacked is
rectangular ($ 0.62 \ \ cm \times 2.03 \ \ cm $) and a height ( $ 1.2
\ \ cm $), all this in order to optimize our experiments adjusted to
all the needs that this required.
  \includegraphics[scale=.5]{Images/SPgrin51}
  \caption{\emph{a) Silicon sample attacked with an electrolytic
      mixture of aqueous hydrofluoric acid (HF) (concentration:
      48 $ \% $  wt), glycerol (purity: 99.8 $ \% $  wt) and
      ethanol (purity: 99.9 $ \% $  wt ) in 3: 7: 1 volume
      ratio, respectively. Obtaining a monolayer of porous
      Silicon with GRIN G1 with an initial current of G1 (5 mA),
      with an attack time of 600s. Three different locations are
      considered, denoted as follows, A (0.3cm) and B (0.8cm)
      and C (1.7cm). b) Reflectance measurements to know the
      optical properties at each of the points and the
      adjustments that were produced by means of the equation
      \ref{Eq:ECMR}. c) We have the indices of refraction of the
      complex porous silicon GRIN, where we calculate the real
      and imaginary part by means of the equation
      \ref{Eq:Brugg}. for different porosities at each point, A
      (P = 0.44), B (P = 0.42) and C (P = 0.40) } }
  \label{fig:DR3}
 The Fig. \ref{fig:DR3} a) three locations at different points are
 considered, denoted as follows, $ A (0.3 \ \ cm) $ and $ B (0.8 \ \
 cm) $ and $ C (1.7 \ \ cm) $, from the sample of PS GRIN $ G1 (I = 5
 mA) $. Also the Fig. \ref{fig:DR3}. b), we have the reflectance
 measurements to know the optical properties and the adjustments that
 were produced by means of the equation \ref{Eq:ECMR}. In the
 Fig. \ref{fig:DR3} c) are indices of refraction of the porous silicon
 complex GRIN, where we calculate the real and imaginary part by means
 of Eq. \ref{Eq:Brugg} for different porosities at each point, $ A (P
 = 0.44) $, $ B (P = 0.42) $ and $ C (P = 0.40) $. Location $ A $ is
 closest to the electrode, while location $ C $ is furthest to the
 other end of the sample. Since the current density is applied from
 one end, the field lines attack the sample laterally to the silicon
 wafer, in the present configuration, an assembly was made based on
 the simulated data shown in Fig. \ref{fig:DR1} the experimental part
 was taken a platinum electrode covering its surface, leaving only a
 very small area, as if it were a tip. The electrochemical reaction
 takes place when we apply currents from an anode end (electrode tip)
 to the silicon substrate (resistivity $ 0.002 - 0.005  \Omega \cdot
 cm $), through an electrolyte forming a current circuit. The
 reflectance spectra of the newly recorded G1 samples measured at
 $ are presented in Fig. \ref{fig:DR3} b), a numerical reflectivity
 adjustment was performed using the transfer matrix method for the
 case of a porous monolayer in Si. It should be noted that the
 adjustment made was considered a spectral range of the wavelength of
 the experimental reflectivity spectra for which the silicon can be
 considered the complex index and thus find the refractive index of
 the complex porous silicon with the purpose of determining the
 porosity and the experimental physical thickness (nm) by means of the
 SEM. The formation of PS GRIN in the thickness occurs due to the
 variation in the concentration of the voids available at the Si
 electrolyte interface, therefore, an increase in the applied lateral
 current density increases the dimension of the pores and their
 depth. Thus, the extent of the porous film showing a gradient that
 can be controlled from the lateral current density.

>>>>

Keywords: Porous Silicon; GRIN; Reflectance Spectra.
\end{abstract}
\notaL{Cambié el abstract, pero habrá que revisarlo después.}
\section{Introduction}
\label{sec:introduction}
\notaL{Debiste poner etiquetas en todas las subsecciones y secciones, y
  ecuaciones y figuras.}
\notaL{No entiendo nada de la introducción}
The structural properties of nanostructured materials  has  received a
considerable attention,  and a large research effort has been devoted
to them \cite{I1}. We found a great way to go for future
technological  explorations,  countless  challenges and  that  open a
range of possibilities to develop further  study  on these
issues\cite{I2}. Porous silicon (PS) is a versatile nanostructured
material and an excellent candidate as a technological platform for
different sensing applications \cite{I3, I4}, due to its easy
manufacturing,  large surface area, high surface reactivity,  and
moreover, its optical transduction capacity.  Photonic crystals are
multilayer dielectric structures that have periodicity in the
dielectric function along one direction \cite{I5}. It has numerous
studies for high reflectivity and the ability to adjust  the photonic
prohibited  band (PBG)\cite{I6} , which leads to possible applications
such as filters\cite{I7}, optical switches\cite{I8}, omnidirectional
mirrors\cite{I9}, waveguides for PC \cite{I10} etc. In the
conventional manufacturing of PS the desired result  is to obtain
homogeneous samples (same structural characteristics) from the
periphery  to the center  of the electrochemically  attacked area.
However, with an asymmetric anodizing configuration,  samples with a
lateral gradient in terms of pore size and thickness of the porous
layer are obtained \cite{I101}. In this configuration,  the face of
the platinum  electrode (cathode)  is relatively maintained
perpendicular  to the surface of the Si substrate (anode) at one end
of the cell, so that the distribution of the current within the
electrolyte  solution varies depending on the distance  of the
electrode due to the resistance of the electrolyte,  resulting  in a
decrease in current density as the distance from the electrode
increases \cite{I102, I103}. The result is a porous surface with
different pore sizes ranging from a few nanometers  to pores on the
order of a few micrometers  \cite{I104}. The dimensions of the pores
obtained on the same chip can be controlled by adjusting the anodizing
current and electrolyte concentration \cite{I11}. Currently, these
types of samples have found their application relevant as optical band
filters \cite{I12}, devices with a multidirectional photonic band
(photonic bar codes) \cite{I13} and mainly as biosensors. In this way,
the effect of different topographies (porosities in the same sample)
on the culture / adhesion of certain cells \cite{I14} is studied,
considerably reducing the number of samples and cost of the study. In
addition, they are also very useful when a biomolecule size-exclusion
technique is required allowing the identification and separation of
these biological compounds \cite{I15}. Recent studies  have shown that
the  combination  of thermal  oxidation  and infiltration of TiO2   by
ALD offers the  opportunity to manufacture  a high index of refraction
of contrast, visibly transparent GRIN optical elements from PS
absorbent structures \cite{I16}. A Despite previous research on the
formation of porous silicon with GRIN, type p in manufacturing and
characterization, there was no control of current densities, much less
a model that  explained said lateral  gradient. In this work, we
reported a gradient refractive index (GRIN) structure by varying the
current density on the fabrication of porous silicon photonic
structure. This current density values, depth, and porosity of the
photonic structure were calculated from an electrostatic model for
photonic crystals with a gradient refractive index
(EMPCGRIN). Moreover, the theoretical and experimental studies were
exhibited similar results.

@@

\section{Theory} \label{sec:theory}
\subsection{Calculation of the current density}
\label{sec:calc-curr-dens}
\notaL{check where acronyms are first defined}
A gradient in the optical properties of porous Silicon (PS) systems may be
obtained by electrochemically attacking a Si surface with a position dependent current
density ${\bm j(\bm r)}$, as the porosity and refractive index depend on
the current density, as well as the speed of attack and the width of the
porous layer. Nevertheless, it is not a simple task to measure the
{\em local} value of $\bm j(\bm r)$ along the surface. This hampers the
design and optimization of well characterized reproducible GRIN PS
structures.\notaL{Tenemos referencias para afirmar esto?} Thus, we
believe a
system for which the current density field may be
easily computed would be useful.
Though $\bm j(\bm r)$ may be in principle be numerically calculated for a
given arbitrary experimental setup,  here we propose a particularly
simple setup that allows an expression for the current in terms
of a series that is rapidly convergent and each of whose terms is a
simple analytic function. With this setup it is easy to characterize
the dependence of different properties of interest on the current, and
this allows the design and optimization of diverse GRIN PS devices.

@@

\section{Procedures}
\label{sec:procedures}
\begin{figure}
  \centering
  \includegraphics[width=.8\textwidth]{paper-3}\\[12pt]
  \includegraphics[width=.8\textwidth]{paper-4}\\[12pt]
  \includegraphics[width=.8\textwidth]{paper-5}
  % \\[12pt]
  % \includegraphics[scale=0.6]{Images/DE1}

@@

\subsection{Fabrication of PS  GRIN Single Layers}
\label{sec:fabrication-ps-grin}
We manufactured single layer PS structures through an electrochemical
anodization on a (100) $p$-type crystalline Si wafer
(resistivity 0.002 - 0.005 $ \Omega\,\text{cm}$), under galvanostatic
conditions. The process was performed at
room temperature,\notaL{Controlaste/mediste la temperatura?} with an
electrolytic mixture of aqueous hydrofluoric
acid (HF) (concentration 48\% wt), glycerol (purity 99.8 \% wt) and
ethanol (purity 99.9\% wt) in a 3:7:1 volume ratio. After the
anodizing process, the samples were rinsed with
ethanol (purity: 99.9 $ \% $  wt). The electrolytic cell had the shape
of a rectangular prism as shown in Fig. \ref{fig:DE1}, with a base of
size $0.62\text{cm}\times2.03\text{cm}$) with an uncovered sample area
of $1.206\text{cm}^2$. \notaL{¿Cuáles fueron las coordenadas del
  electrodo?} We manufactured samples using a current $I=5\text{mA}$
which yielded current densities in the range
$j_\perp=2.5-6.0\text{mA}/\text{cm}^2$ and other smples using a larger
current $I=40\text{mA}$ corresponding to current densities in the
range $j_\perp=20-50\text{mA}/\text{cm}^2$. The cathode was a
platinum wire that with an approximate diameter of $0.5\text{mm}$.
\subsection{Morphological studies}
\label{sec:morph-stud}
\notaL{Cambié el orden}
The morphologies of the etched porous layers were
observed using a Hitachi SU1510 scanning electron microscope (SEM)
with which we measured the thickness $d$ and the porosity $p$ of the
films at different positions along the sample from its top and side
views (Fig. \ref{fig:DE1}).

\subsection{Reflectance Measurement}
\label{sec:refl-meas}
We measured the reflectivity spectra using a {\em Perkin Elmer Lambda 950}
UV-Vis-NIR spectrophotometer. For iterpretation of the data in the
case of a single PS layer we used
the standard formula \notaL{referencia} for three media air (0), PS
(1) and c-Si (2),
 \begin{eqnarray}\label{Eq:ECMR}
   R=\frac{r _ {_ {01}}r _ {_ {12}} e^{2i\delta}}{1+r _ {_ {01}}r _ {_ {12}} e^{2i\delta}}
\end{eqnarray}
where $ r_{01} $ y $ r_{12}$ are the Fresnel reflectance
coefficients at the air/PS and PS/c-Si interfaces \notaL{referencias}
and $\delta=k_{PS}^\perp d$, where $k_{PS}^\perp$ is
the component of the wavevector perpendicular to the surface within
the porous layer of width $d$.
\notaL{Me tienes que explicar dónde y cómo usaste lo que mencionas en
  la siguiente frase:
The advantage of this method is
the possibility of taking into account the interface roughness effect
by including the Davies-Bennett factor in the coefficient of each
Fresnel \cite{I17, I18, I19}, which represents the roughness of a
Gaussian distribution.}

\subsection{Refraction Index of PS GRIN Single Layers}
\label{sec:refraction-index-ps}
The local refractive index $n_{PS}$ of the PS layer was calculated from its
porosity $p$ through
Bruggeman's effective medium theory \cite{I20} \notaL{Elegir y checar:
  varepsilon o epsilon para funciones dieléctricas}
\begin{eqnarray}\label{Eq:Brugg}
 p\frac{1-\varepsilon_{PS}} {1+\varepsilon_{PS}} + (1-p)
  \frac{\varepsilon_{\text{Si}} - \varepsilon_{PS}}
  {\varepsilon_{\text{Si}}+\varepsilon_{PS}}=0
\end{eqnarray}
\notaL{Te faltaba la igualdad}
where the porosity $p$ is the volume fraction of air within the PS
layer, $\varepsilon_{Si}$ is the dielectric function of c-Si, and
$\varepsilon_{PS}=n_{PS}^2$ is the dielectric function of the PS.
\notaL{Quité frases irrelevantes.}
\subsection{Fabrication  of GRIN PS Microcavities}
\label{sec:fabrication-grin-ps}
After characterizing the preparation of single PS GRIN layers, we
fabricated PS GRIN microcavities (MC) as specific defects between two distributed Bragg
mirrors  (DBR). Alternate quarter wavelength plates of high (H) and low (L)
refractive indices $n_i$ of widths $d_i$, $i=H,L$ were prepared satisfying the Bragg condition
$n_id_i=\frac{\lambda_c}{4}$ at a given design
wavelength $\lambda_c$ and at a position $A$ (Fig. \ref{fig:DE1} which
we chose as that directly below the point-like electrode. The defect
was chosen as a half-wavelength low index layer of width $d_d$ such that
$n_Ld_L=\lambda_c/2$, and the MC has the
following sequence: $(HL)_6HH(LH )_6$. \notaL{Hay algo mal. La
  película de $\lambda/2$ fue de alto o de bajo índice? En una parte
  dices una cosa y en otra otra. ¿Será $(HL)_jHLLH(LH)_6$? ¿O será
  $(LH)_6LL(HL)_6$? ¡Muy descuidado!}
We chose $\lambda_c= 0.67 \mu\text{m}$. For the high index layers we
chose a current $I_H=5\text{mA}$ which corresponded to a current density
$j_{HA\perp}= 6\text{mA}/\text{cm}^2$ below the tip \notaL{checar}, and yielded
$n_H =2.6$, corresponding to a porosity \notaL{P mayúscula
  es porosidad, o p minúscula. Checar consistencia} $P_H =0.46$, and a
width $d_H=0.066 \mu\text{m}$, which required an attack time of
$t_H=35 \text{s}$. The corresponding parameters for the low density
layers were $I_L=38\text{mA}$, $j_{LA\perp}=50\text{mA}/\text{cm}^2$, $n_L= 1.4$,  $P_L =0.75$,
$d_L=0.117 \mu \text{m}$, and $t_L=11 \text{s}$. For the rest of the
sample the current density, porosity, index of refraction and width
varied, yielding a GRIN MC.

\section{Discussion and Results}
\label{sec:discussion-results}
\subsection{Current Density}
\label{sec:current-density}
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{Images/G123}
  \caption{Normalized current density $j_\perp(z,0,0)/I$ calculated through
    Eq. (\ref{Eq:J}) for a
    system as in Figs. \ref{f:celda} and \ref{fig:DE1} for a cell of
    length $a = 2.03\text{cm}$ and width $b=0.62\text{cm}$, for a
    point-like electrode at $\bm r_0=(0.2\text{cm},
    0.4\text{cm},0.98\text{cm})$ (top panel). Normalized current
    along the line $y=?$ (bottom panel). \notaL{qué valor de $y$ usaste para la
      gráfica de abajo?} \notaL{Puse $x_0$
      y $y_0$ que faltaban. Checale. Se me hace raro que no esté
      centrado en la celda a lo ancho. ¿No está debería estar en
      $y_0=0.31\text{cm}?$} \notaL{Cambia los letreros, $J$ por
      $j_\perp$. La ordenada no es a, sino $x$ y la abcisa no es b
      sino $y$}. }
  \label{fig:DR1}
\end{figure}
\notaL{Checar consistencia notación. $x_0$, $y_0$ y $z_0$ en
  minúsculas. Igual $j_\perp$.}
In Fig. \ref{fig:DR1} we show the current density $j_\perp(x,y,0)$ calculated through
Eq. \eqref{Eq:J} at the surface of the sample for the cell we built
(see Figs. \ref{f:celda} and \ref{fig:DE1}) with length
$a=2.03\text{cm}$ and width $b = 0.62\text{cm}$, the height of the
solution was taken as $c=1\text{cm}$ and we set the tip of the
electrode at $\bm
r_0=(x_0,y_0,z_0)=(0.2\text{cm},0.4\text{cm},0.96\text{cm})$
\notaL{Descuidado. En la figura dice 0.98, no 0.96}.
\notaL{¿Por qué usaste estos valores?}
\notaL{Esto no es interesante: the programming with the
  PERL PDL package and corresponding graph in gnuplot.}
\notaL{¿Qué significa esto?:We optimize the
appropriate values so that our current density adequately attacks
crystalline silicon, giving the gradient effect.}
For these parameters we obtained $ j_\perp/I\sim
0.5-1.2\text{cm}^{-2}$
\notaL{Quité el resto del párrafo pues no entendí nada.}

\subsection{PS GRIN Single Layer }
\label{sec:ps-grin-single}
\notaL{Quité la figura pues no añade nada}
\notaL{Quité la descripción, pues está arriba}
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{Images/SPgrin51}
  \caption{(a)  Sample $G_1$ prepared as described in
     \ref{sec:fabrication-ps-grin} using a current $I=5 \text{mA}$
    during a time $t=600\text{s}$. We indicate three regions $A$,
    $B$, and $C$ centered at positions at positions,
    $x_A=0.3\text{cm}$ \notaL{Atrás habías dicho que era justo abajo
      del electrodo. ¿Es cierto o no? ¿Dónde estaba el electrodo? ¿Qué
    altura tenía el agua? ¿Igual que en la sección previa?}, $x_B=0.8\text{cm}$ and
    $x_C=1.7\text{cm}$. \notaL{¿Cuánto vale $y$?} (b) Reflectance
    spectra measured at the center of regions $A$, $B$, and $C$ and fit
    using Eq. \eqref{Eq:ECMR}.\notaL{¿Cuáles parámetros se ajustaron y
      cuáles se midieron independientemente}\notaL{Para que no se vean
      tan chicas las figuras, quita las R's y los números en el segundo
      renglon, excepto en el extremo izquierdo, y pega las tres
      figuras una tras la otra. Haz lo mismo en el tercer renglón,
      quitando dos de los letreros Refractive index, pero antes
      asegúrate de usar la misma escala en las tres figuras} (c)
    Corresponding complex indices of refraction $n+ik$ obtained from
    Eq. \eqref{Eq:Brugg} using the fitted porosities $p_A=0.44$,
    $p_B=0.42$, and $p_C= 0.40$ at the chosen positions. \notaL{En las
      figuras escribe A, B y C en lugar de
      Point A, Point B y Point C. Escribe $p_A$, $p_B$ y $p_C$ en lugar
      de la palabra Porosity. Escribe $n$ y $k$ nada más, sin la
      palabra Real ni Imaginary. Usa Theory en lugar de
      Simulation. Usa línea a trazos para la parte
      imaginaria. Alínea todos los letreros. En inglés, los rótulos
      a), b) y c) se escriben como (a), (b) y (c), aunque creo que se
      pueden eliminar (porque además, no los alineaste bien). }
  \notaL{A ojo no se notan las diferencias en epsilon. Mejor junta las
  tres partes reales en una sola gráfica y las tres partes imaginarias
en otra y ponerlas una al lado de la otra.}}
  \label{fig:DR3}
\end{figure}
 In Fig. \ref{fig:DR3} we show a photograph of one of our single layer PS GRIN
 structures, $G_1$, prepared as described in
 \ref{sec:fabrication-ps-grin} applying a current $I=5\text{mA}$ for
 $t=600\text{s}$. We employed the same geometry as described in
 Sec. \ref{sec:current-density} \notaL{Lo inventé. ¿Es cierto?}
The position of electrode corresponds to the upper left side of the
photograph. The variation of the optical properties across the
sample is evident. We chose three positions $x_A=0.3\text{cm}$,
$x_B=0.8\text{cm}$ and $x_C=1.7\text{cm}$ \notaL{¿valor de y?} on
which we measured the reflectance spectra, also shown in the figure.
We fitted the measurements using Eqs. \eqref{Eq:ECMR} and
\eqref{Eq:Brugg} using the local porosity and the depth of the layer
as adjustable parameters. We obtained $p_A=0.44$, $p_B=0.42$, and
$p_C= 0.40$. \notaL{Falta decir cuáles fueron las profundidades}
Location $A$ is
closest to the electrode, while location $ C $ is the furthest.
\notaL{Quité una frase sin sentido.}
We also show in Fig. \ref{fig:DR3} the wavelength dependence of
 the complex index of refraction corresponding to the fitted porosities.
\notaL{Quité otra frase que no entendí, pero que me generó una duda:
  la profundidad la ajustaste ópticamente o la mediste en SEM y luego
  hiciste el ajuste a la reflectancia?}
